Guilt, shame, and anti-war action in an authoritarian country at war

### 2023-04-28 manuscript.Rmd
Added docker resources

h5 <- zeroinfl(fb_oppos_count ~ posem+neg_dom+neg_sub+smop_att+
                 +mshamef+ishamef+cguiltf,d3,dist="negbin")
summary(h5)

@@

The results of the zero-inflated negative binomial model (Table \@ref(tab:TableS4), SM) suggested that different predictors account for the presence vs. absence of intentions to act versus the strength of these intentions. Only moral shame (*b* = -.36, *p* = .036) and attitude (*b* = .38, *p* = .001) predicted the probability of no action, whereas only negative emotions predicted the strength of these intentions. Negative dominant emotions predicted stronger intentions to act (*b* = .24, *p* < .001), whereas negative submissive emotions predicted weaker intentions to act (*b* = -.14, *p* = .013).

@@

S4 <- summary(h5)

>>>>

h5 <- zeroinfl(fb_oppos_count ~ posem+neg_dom+neg_sub+smop_att+
                 +mshamef+ishamef+cguiltf,d3,dist="negbin")
summary(h5)
S4 <- summary(h5)

@@

The results of the zero-inflated negative binomial model (Table \@ref(tab:TableS4), SM) suggested that different predictors account for the presence vs. absence of intentions to act versus the strength of these intentions. Only moral shame (*b* = `r round(S4$coefficients$zero[6,1],digits=2)`, *p* = `r round(S4$coefficients$zero[6,4],digits=3)`) and attitude (*b* = `r round(S4$coefficients$zero[5,1],digits=2)`, *p* = `r round(S4$coefficients$zero[5,4],digits=3)`) predicted the probability of no action, whereas only negative emotions predicted the strength of these intentions. Negative dominant emotions predicted stronger intentions to act (*b* = `r round(S4$coefficients$count[3,1],digits=2)`, *p* = <0.001), whereas negative submissive emotions predicted weaker intentions to act (*b* = `r round(S4$coefficients$count[4,1],digits=2)`, *p* = `r round(S4$coefficients$count[4,4],digits=3)`).

@@

### 2023-04-28 manuscript.tex
Added docker resources

The results of the zero-inflated negative binomial model (Table \ref{tab:TableS4}, SM) suggested that different predictors account for the presence vs.~absence of intentions to act versus the strength of these intentions. Only moral shame (\emph{b} = -.36, \emph{p} = .036) and attitude (\emph{b} = .38, \emph{p} = .001) predicted the probability of no action, whereas only negative emotions predicted the strength of these intentions. Negative dominant emotions predicted stronger intentions to act (\emph{b} = .24, \emph{p} \textless{} .001), whereas negative submissive emotions predicted weaker intentions to act (\emph{b} = -.14, \emph{p} = .013).

>>>>

The results of the zero-inflated negative binomial model (Table \ref{tab:TableS4}, SM) suggested that different predictors account for the presence vs.~absence of intentions to act versus the strength of these intentions. Only moral shame (\emph{b} = -0.36, \emph{p} = 0.036) and attitude (\emph{b} = 0.38, \emph{p} = 0.001) predicted the probability of no action, whereas only negative emotions predicted the strength of these intentions. Negative dominant emotions predicted stronger intentions to act (\emph{b} = 0.24, \emph{p} = \textless0.001), whereas negative submissive emotions predicted weaker intentions to act (\emph{b} = -0.14, \emph{p} = 0.013).
